\wititle{General Knowledge}{}

\witqstart{gk}{General Knowledge}

\txtq{Which film was the first of Walt Disney's "golden age"?}{Snow White}{Lion King}{Dumbo}{Pinocchio}{Die Hard}
\txtq{Which nationality was the polar explorer Roald Amundsen?}{Norwegian}{Swedish}{Dutch}{Guatemalen}{Finnish}
\txtq{In which year did Britain originally join the EEC, now known as the European Union?}{1973}{1983}{1975}{1968}{1970}
\txtq{In Netflix's "Tiger King", what is the name of Carole Baskin's second husband who many believe she fed to the tigers?}{Don Lewis}{Joe Exotic}{Doc Antle}{Rick Kirkham}{Eric Goode}
\txtq{What was David Bowie's real name?}{David Jones}{David Smith}{David Brown}{David de Groot}{HRH Prince David St.~John-Smythe of Wolverhampton}
\txtq{Taylor Swift grew up on what type of farm?}{Christmas Tree}{Sheep}{Dairy}{Pig}{Salmon}
\txtq{What colour is found on 75\% of the world’s national flags?}{Red}{Blue}{White}{Green}{Hot Pink}
\txtq{Which fictional wizard said: "It does not do to dwell on dreams and forget to live?"}{Albus Dumbledore}{Newt Scamander}{Gandalf}{Merlin}{Tim The Enchanter}

\witqend

\witqstart{gk}{General Knowledge}

\txtq{What is the chemical symbol for gold?}{Au}{Ag}{Go}{Na}{Ni}
\txtq{What is Lady Gaga's real name?}{Stephanie}{Sarah}{Jane}{Laura}{Violet}
\txtq{How tall is the Eiffel Tower?}{324m}{380m}{295m}{302m}{363m}
\txtq{What is the middle name of Angela Merkel?}{Dorothea}{Mutti}{Leonie}{Johanna}{Lina}
\txtq{Which bird can fly backwards?}{Hummingbird}{Penguin}{Raven}{Booted Eagle}{Cardinal}
\txtq{What do you call a group of jellyfish?}{A bloom}{A disaster}{A swarm}{A school}{A gathering}
\txtq{How many legs does a lobster have?}{8}{6}{4}{10}{2}
\txtq{How much wood would a woodchuck chuck if a woodchuck could chuck wood?}{ZOT!}{1 lb}{2 kg}{4 board-acres}{12 cords}

\witqend

\witqstart{gk}{General Knowledge}

\txtq{What is the chemical symbol for Gallium?}{Ga}{Gn}{Gl}{Pb}{Au}
\txtq{GalliumOS is for what kind of hardware?}{Cr}{Fe}{Si}{Ga}{Au}
\txtq{Gallium was the IRC nick of which KDE contributor? (First initial)}{K}{C}{H}{O}{N}
\txtq{The melting point of Gallium is, to the nearest degree Centigrade}{30}{28}{29}{31}{451}
\txtq{Who live in the Gallic village?}{The Gauls}{The Gals}{John Galt}{Garth Brooks}{The Grinch}
\txtq{Gallflies are in which subgroup of the insects?}{Hymenoptera}{Blattodea}{Mantodea}{Diptera}{Zygentoma}
\txtq{A galloping tapir can reach ...}{48 km/h}{3 km/h}{16 km/h}{24 km/h}{0.9c}
\txtq{The last gallows in England was in ...}{Wandsworth}{Hogwarts}{Quittich}{Stavesbury}{Rodneys Isle}

\witqend
