\wititle{Places}{}

\witqstart{places}{Places}

\newbox\doner\setbox\doner\hbox{D\"oner}
\newbox\coruna\setbox\coruna\hbox{\'A Coru\~na}
% \newbox\nurnberg\setbox\nurnberg\hbox{N\"urnberg}
\txtq{Where was the most northern location for Akademy?}{Tampere}{Tallinn}{Glasgow}{Berlin}{Gran Canaria}
\txtq{To the nearest 100, what is the population of Mechelen in Belgium?}{86,300}{48,700}{58,200}{90,100}{74,200}
\txtq{Glasgow is twinned with which German city?}{N\"urnberg}{Köln}{Hannover}{Frankfurt}{Essen}
\txtq{\copy\coruna~ has a lighthouse dedicated to which hero?}{Hercules}{Oddyseus}{Janus}{Adriaan de Groot}{Quirinus}
\txtq{Every day Berliners consume roughly how much \copy\doner~meat?}{60 tonnes}{48 tonnes}{259 tonnes}{7 tonnes}{12 tonnes}
\txtq{In Brno, the cathedral is dedicated to which saints?}{St.~Peter and St.~Paul}{St.~George and St.~John}{St.~Michael and St.~Sithney}{St.~Christopher and St.~Margaret}{St.~Helen and St.~Sebastian}
\txtq{Gran Canaria is the 3rd largest of the Canary Islands. Which is the largest?}{Tenerife}{Fuerteventura}{Lanzarote}{La Palma}{La Gomera}
\txtq{Malaga is home to how many wineries?}{45}{8}{4}{16}{12}
\txtq{In Tampere 2009, Paul, Ade and Claudia attended a gig from a band called "The Dirty Dealers". But what was the name of the venue?}{Jack the Rooster}{John the Cockerel}{Simon the Puffin}{Charles the Chestnut-shouldered Antwren}{Rick the Robin}
\txtq{Two rivers flow through Bilbao: Ibaizabal and...?}{Nervión}{Ebro}{Tagus}{Minho}{Bidasoa}

\witqend
